\documentclass[a4paper,10pt]{article}

% Package imports
\usepackage[left=0.5in, right=0.5in, top=0.3in, bottom=0.2in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}

% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}

\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}


\pagestyle{empty}

\begin{document}

%----------------------------------------------------------------------------------------
% HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \textbf{ABIR GUPTA}} \\ \vspace{4pt}
    \href{mailto:abir.guptaaa@gmail.com}{abir.guptaaa@gmail.com} \ | \ +91-88245-37921 \\
    \href{https://linkedin.com/in/abirxgpt}{linkedin.com/in/abirxgpt} \ | \
    \href{https://github.com/abirxgpt}{github.com/abirxgpt} \ | \
    \href{https://portfolio-abir-liard.vercel.app/}{Portfolio} 
\end{center}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Machine Learning and Deep Learning Engineer with strong research experience in computer vision, NLP, and explainable AI. Proven ability to design hybrid models, fine-tune LLMs, build RAG pipelines, and deliver end-to-end AI systems. Seeking an Assistant Software Developer or ML Engineer role.

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{Government Engineering College, Ajmer} \hfill Nov 2022 -- May 2026 \\
Bachelor of Technology (B.Tech) in Computer Science and Engineering \hfill \textbf{CGPA: 8.56}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

\textbf{AI Engineer} \hfill Feb 2026 -- Present \\
\textit{OXMAINT AI}
\begin{itemize}[noitemsep, leftmargin=*, topsep=2pt]
    \item Built n8n-based automation workflows integrating a personal API layer for open-source LLMs running on NVIDIA DGX infrastructure, enabling scalable self-hosted AI pipelines.
    \item Developed an OCR pipeline for CMS lists and documents, automating structured data extraction and improving document processing efficiency.
    \item Designed and deployed a Vision Language Model (VLM) system with prompt engineering to produce reliable, structured JSON outputs for downstream AI workflows.
    \item Built an automated RAG-powered lead finder and outreach system that identifies prospects, generates personalized messages, and sends LinkedIn connection requests autonomously.
\end{itemize}

\vspace{2pt}

\textbf{Research Intern (Machine Learning \& Computer Vision)} \hfill May 2025 -- Oct 2025 \\
\textit{Malaviya National Institute of Technology (MNIT), Jaipur}
\begin{itemize}[noitemsep, leftmargin=*, topsep=2pt]
    \item Developed a bilingual (Hindi/English) XAI-based annotation tool for frame-level deepfake artifact labeling with spatial-temporal explainability.
    \item Designed a hybrid deepfake detection architecture (TCAN-STIL) combining Transformers and CNNs, achieving improved temporal-spatial accuracy on benchmark datasets.
    \item Curated the HiSAG dataset with 13K+ Hindi news samples and AI-generated variants using GPT-4 and Gemini to support low-resource text detection.
    \item Built the HID-DF deepfake benchmark comprising 1,200 Indian videos to mitigate demographic bias in existing deepfake datasets.
\end{itemize}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\textbf{SQL Copilot — Natural Language to SQL System (Local AI)} \hfill Oct 2025 -- Present \\
\begin{itemize}[noitemsep, leftmargin=*, topsep=.5pt]
    \item Built a production-ready NL2SQL system using local LLMs (Ollama + Qwen2.5-Coder) for offline natural language to SQL conversion without paid APIs.
    \item Designed a schema-aware RAG pipeline with ChromaDB, reducing context size by 63\% and improving query accuracy and execution reliability.
    \item Developed a FastAPI backend and React frontend with SQL validation, error correction, query explanation, and interactive data visualization.
\end{itemize}

\vspace{2pt}

\textbf{Fine-Tuning LLaMA 3 on Osho Discourses} \hfill Jan 2025 -- Mar 2025 \\
\begin{itemize}[noitemsep, leftmargin=*, topsep=.5pt]
    \item Fine-tuned Meta's LLaMA 3 on philosophical discourse data; implemented a RAG pipeline to improve factual consistency and reduce hallucinations.
    \item Optimized data preprocessing and inference pipelines to enhance response quality and latency.
\end{itemize}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{itemize}[noitemsep, leftmargin=*, topsep=2pt]
    \item \textbf{Programming:} Python, Java, C, SQL
    \item \textbf{ML / DL:} CNN, Transformers, GANs, U-Net, LSTM, RAG, Fine-Tuning, LLMs, VLMs, Supervised \& Unsupervised Learning
    \item \textbf{NLP \& CV:} Hugging Face, OpenCV, MediaPipe, Tokenization, Image Segmentation
    \item \textbf{Tools \& Infra:} TensorFlow, PyTorch, FastAPI, n8n, ChromaDB, Ollama, NVIDIA DGX, Git, Google Colab
\end{itemize}

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section{Achievements}
\begin{itemize}[noitemsep, leftmargin=*, topsep=2pt]
    \item \textbf{Leadership:} Secretary and Vice President, Programming and Competitive Coding Club (PCC); organized coding workshops and intra-college hackathons.
    \item \textbf{SQL Excellence:} Global Rank 1 in SQL on HackerRank (2024). \textbf{Gold Medal} in Python Programming by HackerRank.
\end{itemize}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications \& Seminars}
\begin{itemize}[noitemsep, leftmargin=*, topsep=2pt]
    \item SQL — HackerRank \ | \ Deep Learning Specialization — deeplearning.ai \ | \ Artificial Intelligence and Machine Learning — RCAT Seminar
\end{itemize}

\end{document}